Latitudinal gradients in biotic niche breadth vary across ecosystem types

### 2018-09-04 manuscript/correction.tex
fixed the apostrophe'
fixing figure refs for manuscript central
resubmitted correction'

    A subset of food webs analysed for this manuscript (75 out of 263; see \emph{Table S2, Appendix S1} for details) had formatting errors or irregularities that caused them to be incorrectly processed by our original code. Some food webs had inconsistent labels that prevented sets of predators and prey from being correctly linked to the same species. Others listed interactions using categorical symbols; these interactions were not included in our original analyses.

@@

\begin{table}[h!]
\caption{Original and corrected values for correlations, mean generalities, and a student's T-test for differences in mean generalities reported in the main text. The 'Location' column indicates the section in which the relationship is described. Original values are those given in the original publication of this article. Corrected values are those obtained after correcting formatting inconsistencies in several food webs.}
\label{corr_comparison}
\small
\begin{tabular}{l l | r | r}
Relationship & Location & Original & Corrected \\
\hline
$R^2_{link density:generality}$ & Results & 0.891 & 0.915 \\
$R^2_{link density:vulnerability}$ & Results & \textgreater0.999 & \textgreater0.999 \\
$R^2_{generality:vulnerability}$ & Results & 0.890 & 0.912 \\
$\mu_{generality_{Aquatic}}$ & Discussion & 5.47 & 5.86 \\
$\mu_{generality_{Terrestrial}}$ & Discussion & 3.82 & 3.75 \\
P($\mu_{generality_{Aquatic}}>\mu_{generality_{Terrestrial}}$) & Discussion & 0.007 & \textless0.001 \\
\end{tabular}
\end{table}

@@

\begin{figure}[h]
% \includegraphics*[width=\textwidth]{Figures/Figure2.eps}
\includegraphics*[width=.48\textwidth]{Figures/Figure2.eps}
\hspace{.02\textwidth}
\includegraphics*[width=.48\textwidth]{Figures/Figure2_updated.eps}

\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
relative to the species richness of a food web. Here we show the original relationships (left)
and the relationships after correcting several food webs (right). Link density, generality,
and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
type. As these relationships take the form of power laws, we did this by dividing the food-web
property (e.g. link density) by species richness raised to an exponent including the 
effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
type and latitude. Note that in all cases estuarine food webs were treated as the baseline 
ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
latitude retained in the best-fit model (see \emph{Results} for specifics). For each relationship, 
we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
ecosystems as a baseline (black line, N=196 food webs). For a figure with the uncorrected values,
see Fig.~\emph{S7}, \emph{Appendix S4}. Note that the corrected and original relationships are 
very similar, but the re-scaled values for some food webs have changed.
}
\label{props_v_lat1}
\end{figure}

\begin{figure}[h]
\includegraphics*[width=.48\textwidth]{Figures/Figure3.eps}
\hspace{.02\textwidth}
\includegraphics*[width=.48\textwidth]{Figures/Figure3_updated.eps}
% \includegraphics*[width=\textwidth]{Figure3.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability with species richness 
across ecosystem types and over latitude. Here we show these changes for the original dataset (left) 
and after correcting several food webs (right). We show the estimated scaling exponent for species 
richness (black line) with its 95\% confidence interval (in grey), based on N=196 empirical food 
webs. Latitude is given in degrees from the equator regardless of direction. Note that the scaling
relationships with latitude were very similar for the original and corrected datasets.} 
\label{S1} 
\end{figure}

% \clearpage

% \section*{Corrected Figures}

% \setcounter{figure}{1}
% \begin{figure}[h]
% % \includegraphics*[width=\textwidth]{Figures/Figure2_updated.eps}
% \includegraphics*[width=\textwidth]{Figure2_updated.eps}
% \caption{
% Figure 2 caption correct in original.}
% \label{props_v_lat}
% \end{figure}

% \begin{figure}[h]
% % \includegraphics*[width=\textwidth]{Figures/Figure3_updated.eps}
% \includegraphics*[width=\textwidth]{Figure3_updated.eps}
% \caption{Figure 3 caption correct in original.} \label{S} \end{figure}

>>>>

    A subset of food webs analysed for the manuscript \emph{Latitudinal gradients in biotic niche breadth vary across ecosystem types}; doi: 10.1098/rspb.2015.1589 had formatting errors or irregularities that caused them to be incorrectly processed by our original code (75 out of 263; see \emph{Table S2, Appendix S1} for details). Some food webs had inconsistent labels that prevented sets of predators and prey from being correctly linked to the same species. Others listed interactions using categorical symbols; these interactions were not included in our original analyses.

@@

\begin{table}[h!]
\caption{Original and corrected values for correlations, mean generalities, and a student's T-test for differences in mean generalities reported in the main text. The `Location' column indicates the section in which the relationship is described. Original values are those given in the original publication of this article. Corrected values are those obtained after correcting formatting inconsistencies in several food webs.}
\label{corr_comparison}
\small
\begin{tabular}{l l | r | r}
Relationship & Location & Original & Corrected \\
\hline
$R^2_{link density:generality}$ & Results & 0.891 & 0.915 \\
$R^2_{link density:vulnerability}$ & Results & \textgreater0.999 & \textgreater0.999 \\
$R^2_{generality:vulnerability}$ & Results & 0.890 & 0.912 \\
$\mu_{generality_{Aquatic}}$ & Discussion & 5.47 & 5.86 \\
$\mu_{generality_{Terrestrial}}$ & Discussion & 3.82 & 3.75 \\
P($\mu_{generality_{Aquatic}}>\mu_{generality_{Terrestrial}}$) & Discussion & 0.007 & \textless0.001 \\
\end{tabular}
\end{table}

@@

\begin{figure}[h]
\includegraphics*[width=.48\textwidth]{Figure2.eps}
\hspace{.02\textwidth}
\includegraphics*[width=.48\textwidth]{Figure2_updated.eps}
\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
relative to the species richness of a food web. Here we show the original relationships (left)
and the relationships after correcting several food webs (right). Link density, generality,
and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
type. As these relationships take the form of power laws, we did this by dividing the food-web
property (e.g. link density) by species richness raised to an exponent including the 
effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
type and latitude. Note that in all cases estuarine food webs were treated as the baseline 
ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
latitude retained in the best-fit model (see \emph{Results} for specifics). For each relationship, 
we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
ecosystems as a baseline (black line, N=196 food webs). For a figure with the uncorrected values,
see Fig.~\emph{S7}, \emph{Appendix S4}. Note that the corrected and original relationships are 
very similar, but the re-scaled values for some food webs have changed.
}
\label{props_v_lat1}
\end{figure}

\begin{figure}[h]
\includegraphics*[width=.48\textwidth]{Figure3.eps}
\hspace{.02\textwidth}
\includegraphics*[width=.48\textwidth]{Figure3_updated.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability with species richness 
across ecosystem types and over latitude. Here we show these changes for the original dataset (left) 
and after correcting several food webs (right). We show the estimated scaling exponent for species 
richness (black line) with its 95\% confidence interval (in grey), based on N=196 empirical food 
webs. Latitude is given in degrees from the equator regardless of direction. Note that the scaling
relationships with latitude were very similar for the original and corrected datasets.} 
\label{S1} 
\end{figure}

### 2018-09-04 manuscript/erratum_letter.tex
resubmitted correction'

\begin{letter}{\bf Professor Spencer C.H. Barrett\\
               Editor-in-Chief\\
               Proceedings of the Royal Society B\\
               6-9 Carlton House Terrace\\
               London, UK\\
               SW1Y 5AG\\
                }

\opening{Dear Prof. Barrett:}

I am writing regarding my article \emph{Latitudinal gradients in biotic niche breadth vary across ecosystem types.} (article ID \#RSPB-2015-1589.R2). The full citation details for this article are: Cirtwill, A.R., Stouffer, D.B., \& Romanuk, T.N. (2015) \emph{Latitudinal gradients in biotic niche breadth vary across ecosystem types}. \textbf{Proceedings of the Royal Society B}: 282(1819), 20151589. doi: 10.1098/rspb.2015.1589

As requested, we have revised our correction by adding a section to explicitly state the purpose of the correction. In this description we refer to \emph{Table S2}, which details the food webs that were corrected and the reason for the correction. We agree with the Editor that our previous submission required a lot of effort from a reader; we had used the ''Original text'', ''Revised text'' format in response to a specific request when we first attempted to submit the correction. In the absence of any guidelines as to how corrections should be formatted, we hope that our current approach will be more user-friendly. We give the results and discussion only once, with original values presented in struck-through font and corrected values immediately following in bold. We believe that this will allow readers to see at a glance that the changes to our results are quite minor.

>>>>

\begin{letter}{\bf Dr. Daniel Costa\\
               Associate Editor\\
               Proceedings of the Royal Society B\\
               6-9 Carlton House Terrace\\
               London, UK\\
               SW1Y 5AG\\
                }

\opening{Dear Dr. Costa:}

We are pleased to submit a revision to our correction to article \emph{Latitudinal gradients in biotic niche breadth vary across ecosystem types.} (article ID \#RSPB-2015-1589.R2). The full citation details for this article are: Cirtwill, A.R., Stouffer, D.B., \& Romanuk, T.N. (2015) \emph{Latitudinal gradients in biotic niche breadth vary across ecosystem types}. \textbf{Proceedings of the Royal Society B}: 282(1819), 20151589. doi: 10.1098/rspb.2015.1589

As requested, we have revised our correction by adding a section to explicitly state the purpose of the correction. In this description we refer to \emph{Table S2}, which details the food webs that were corrected and the reason for the correction. We have also restructured our correction in an effort to be more user-friendly. We agree with the Editor that our previous submission required a lot of effort from a reader; we had used the ''Original text'', ''Revised text'' format in response to a specific request when we first attempted to submit the correction. In the absence of any guidelines as to how corrections should be formatted, we now present only the corrected text (with any changes highlighted in bold). The original and corrected values for all changes are now presented in two tables which are referred to in the text. We hope that this will allow readers to see what has changed with minimal searching. We also now show the original and corrected figures side-by-side to illustrate both the minor changes to some data points and the consistency of the overall relationships reported. We believe that these changes will make it easy for any reader to see exactly what has changed and that our original conclusions hold. If the Editor has any further specific formatting changes that he would like us to implement, we are happy to do so.
